A closer look at fixed effects regression in structural equation modeling using \texttt{lavaan}

### 2021-01-14 article_format/article_format.tex
Started major changes for resubmission

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{a =}\ErrorTok{~}\StringTok{ }\DecValTok{1}\OperatorTok{*}\NormalTok{y1 }\OperatorTok{+}\StringTok{ }\DecValTok{1}\OperatorTok{*}\NormalTok{y2 }\OperatorTok{+}\StringTok{ }\DecValTok{1}\OperatorTok{*}\NormalTok{y3 }\OperatorTok{+}\StringTok{ }\DecValTok{1}\OperatorTok{*}\NormalTok{y4 }\OperatorTok{+}\StringTok{ }\DecValTok{1}\OperatorTok{*}\NormalTok{y5}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{y1 }\OperatorTok{~}\StringTok{ }\NormalTok{b}\OperatorTok{*}\NormalTok{x1}
\NormalTok{y2 }\OperatorTok{~}\StringTok{ }\NormalTok{b}\OperatorTok{*}\NormalTok{x2 }
\NormalTok{y3 }\OperatorTok{~}\StringTok{ }\NormalTok{b}\OperatorTok{*}\NormalTok{x3}
\NormalTok{y4 }\OperatorTok{~}\StringTok{ }\NormalTok{b}\OperatorTok{*}\NormalTok{x4}
\NormalTok{y5 }\OperatorTok{~}\StringTok{ }\NormalTok{b}\OperatorTok{*}\NormalTok{x5}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{a }\OperatorTok{~}\ErrorTok{~}\StringTok{ }\NormalTok{x1 }\OperatorTok{+}\StringTok{ }\NormalTok{x2 }\OperatorTok{+}\StringTok{ }\NormalTok{x3 }\OperatorTok{+}\StringTok{ }\NormalTok{x4 }\OperatorTok{+}\StringTok{ }\NormalTok{x5}
\NormalTok{x1 }\OperatorTok{~}\ErrorTok{~}\StringTok{ }\NormalTok{x2 }\OperatorTok{+}\StringTok{ }\NormalTok{x3 }\OperatorTok{+}\StringTok{ }\NormalTok{x4 }\OperatorTok{+}\StringTok{ }\NormalTok{x5}
\NormalTok{x2 }\OperatorTok{~}\ErrorTok{~}\StringTok{ }\NormalTok{x3 }\OperatorTok{+}\StringTok{ }\NormalTok{x4 }\OperatorTok{+}\StringTok{ }\NormalTok{x5}
\NormalTok{x3 }\OperatorTok{~}\ErrorTok{~}\StringTok{ }\NormalTok{x4 }\OperatorTok{+}\StringTok{ }\NormalTok{x5}
\NormalTok{x4 }\OperatorTok{~}\ErrorTok{~}\StringTok{ }\NormalTok{x5}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{y1 }\OperatorTok{~}\ErrorTok{~}\StringTok{ }\NormalTok{e}\OperatorTok{*}\NormalTok{y1}
\NormalTok{y2 }\OperatorTok{~}\ErrorTok{~}\StringTok{ }\NormalTok{e}\OperatorTok{*}\NormalTok{y2}
\NormalTok{y3 }\OperatorTok{~}\ErrorTok{~}\StringTok{ }\NormalTok{e}\OperatorTok{*}\NormalTok{y3}
\NormalTok{y4 }\OperatorTok{~}\ErrorTok{~}\StringTok{ }\NormalTok{e}\OperatorTok{*}\NormalTok{y4}
\NormalTok{y5 }\OperatorTok{~}\ErrorTok{~}\StringTok{ }\NormalTok{e}\OperatorTok{*}\NormalTok{y5}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{fe_sem <-}\StringTok{ '}
\StringTok{# Define individual effects variable }
\StringTok{a =~ 1*y1 + 1*y2 + 1*y3 + 1*y4 + 1*y5}
\StringTok{# Regressions, constrain coefficient to be equal over time}
\StringTok{y1 ~ b*x1}
\StringTok{y2 ~ b*x2 }
\StringTok{y3 ~ b*x3}
\StringTok{y4 ~ b*x4}
\StringTok{y5 ~ b*x5}
\StringTok{# Allow unrestricted correlation between eta and covariates}
\StringTok{a ~~ x1 + x2 + x3 + x4 + x5}
\StringTok{x1 ~~ x2 + x3 + x4 + x5}
\StringTok{x2 ~~ x3 + x4 + x5}
\StringTok{x3 ~~ x4 + x5}
\StringTok{x4 ~~ x5}
\StringTok{# Constrain residual variances to be equal over time}
\StringTok{y1 ~~ e*y1}
\StringTok{y2 ~~ e*y2}
\StringTok{y3 ~~ e*y3}
\StringTok{y4 ~~ e*y4}
\StringTok{y5 ~~ e*y5}
\StringTok{'}
\NormalTok{fe_sem.fit <-}\StringTok{ }\KeywordTok{sem}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ fe_sem, }
                  \DataTypeTok{data =}\NormalTok{ dfw, }
                  \DataTypeTok{estimator =} \StringTok{"ML"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(fe_sem.fit)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## lavaan 0.6-6 ended normally after 37 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of free parameters                         31
##   Number of equality constraints                     8
##                                                       
##   Number of observations                          1000
##                                                       
## Model Test User Model:
##                                                       
##   Test statistic                                30.138
##   Degrees of freedom                                32
##   P-value (Chi-square)                           0.561
## 
## Parameter Estimates:
## 
##   Standard errors                             Standard
##   Information                                 Expected
##   Information saturated (h1) model          Structured
...
\end{verbatim}

>>>>

% Pandoc citation processing

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{a =}\ErrorTok{\textasciitilde{}}\StringTok{ }\DecValTok{1}\OperatorTok{*}\NormalTok{y1 }\OperatorTok{+}\StringTok{ }\DecValTok{1}\OperatorTok{*}\NormalTok{y2 }\OperatorTok{+}\StringTok{ }\DecValTok{1}\OperatorTok{*}\NormalTok{y3 }\OperatorTok{+}\StringTok{ }\DecValTok{1}\OperatorTok{*}\NormalTok{y4 }\OperatorTok{+}\StringTok{ }\DecValTok{1}\OperatorTok{*}\NormalTok{y5}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{y1 }\OperatorTok{\textasciitilde{}}\StringTok{ }\NormalTok{b}\OperatorTok{*}\NormalTok{x1}
\NormalTok{y2 }\OperatorTok{\textasciitilde{}}\StringTok{ }\NormalTok{b}\OperatorTok{*}\NormalTok{x2 }
\NormalTok{y3 }\OperatorTok{\textasciitilde{}}\StringTok{ }\NormalTok{b}\OperatorTok{*}\NormalTok{x3}
\NormalTok{y4 }\OperatorTok{\textasciitilde{}}\StringTok{ }\NormalTok{b}\OperatorTok{*}\NormalTok{x4}
\NormalTok{y5 }\OperatorTok{\textasciitilde{}}\StringTok{ }\NormalTok{b}\OperatorTok{*}\NormalTok{x5}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{a }\OperatorTok{\textasciitilde{}}\ErrorTok{\textasciitilde{}}\StringTok{ }\NormalTok{x1 }\OperatorTok{+}\StringTok{ }\NormalTok{x2 }\OperatorTok{+}\StringTok{ }\NormalTok{x3 }\OperatorTok{+}\StringTok{ }\NormalTok{x4 }\OperatorTok{+}\StringTok{ }\NormalTok{x5}
\NormalTok{x1 }\OperatorTok{\textasciitilde{}}\ErrorTok{\textasciitilde{}}\StringTok{ }\NormalTok{x2 }\OperatorTok{+}\StringTok{ }\NormalTok{x3 }\OperatorTok{+}\StringTok{ }\NormalTok{x4 }\OperatorTok{+}\StringTok{ }\NormalTok{x5}
\NormalTok{x2 }\OperatorTok{\textasciitilde{}}\ErrorTok{\textasciitilde{}}\StringTok{ }\NormalTok{x3 }\OperatorTok{+}\StringTok{ }\NormalTok{x4 }\OperatorTok{+}\StringTok{ }\NormalTok{x5}
\NormalTok{x3 }\OperatorTok{\textasciitilde{}}\ErrorTok{\textasciitilde{}}\StringTok{ }\NormalTok{x4 }\OperatorTok{+}\StringTok{ }\NormalTok{x5}
\NormalTok{x4 }\OperatorTok{\textasciitilde{}}\ErrorTok{\textasciitilde{}}\StringTok{ }\NormalTok{x5}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{y1 }\OperatorTok{\textasciitilde{}}\ErrorTok{\textasciitilde{}}\StringTok{ }\NormalTok{e}\OperatorTok{*}\NormalTok{y1}
\NormalTok{y2 }\OperatorTok{\textasciitilde{}}\ErrorTok{\textasciitilde{}}\StringTok{ }\NormalTok{e}\OperatorTok{*}\NormalTok{y2}
\NormalTok{y3 }\OperatorTok{\textasciitilde{}}\ErrorTok{\textasciitilde{}}\StringTok{ }\NormalTok{e}\OperatorTok{*}\NormalTok{y3}
\NormalTok{y4 }\OperatorTok{\textasciitilde{}}\ErrorTok{\textasciitilde{}}\StringTok{ }\NormalTok{e}\OperatorTok{*}\NormalTok{y4}
\NormalTok{y5 }\OperatorTok{\textasciitilde{}}\ErrorTok{\textasciitilde{}}\StringTok{ }\NormalTok{e}\OperatorTok{*}\NormalTok{y5}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{fe\_sem \textless{}{-}}\StringTok{ \textquotesingle{}}
\StringTok{\# Define individual effects variable }
\StringTok{a =\textasciitilde{} 1*y1 + 1*y2 + 1*y3 + 1*y4 + 1*y5}
\StringTok{\# Regressions, constrain coefficient to be equal over time}
\StringTok{y1 \textasciitilde{} b*x1}
\StringTok{y2 \textasciitilde{} b*x2 }
\StringTok{y3 \textasciitilde{} b*x3}
\StringTok{y4 \textasciitilde{} b*x4}
\StringTok{y5 \textasciitilde{} b*x5}
\StringTok{\# Allow unrestricted correlation between eta and covariates}
\StringTok{a \textasciitilde{}\textasciitilde{} x1 + x2 + x3 + x4 + x5}
\StringTok{x1 \textasciitilde{}\textasciitilde{} x2 + x3 + x4 + x5}
\StringTok{x2 \textasciitilde{}\textasciitilde{} x3 + x4 + x5}
\StringTok{x3 \textasciitilde{}\textasciitilde{} x4 + x5}
\StringTok{x4 \textasciitilde{}\textasciitilde{} x5}
\StringTok{\# Constrain residual variances to be equal over time}
\StringTok{y1 \textasciitilde{}\textasciitilde{} e*y1}
\StringTok{y2 \textasciitilde{}\textasciitilde{} e*y2}
\StringTok{y3 \textasciitilde{}\textasciitilde{} e*y3}
\StringTok{y4 \textasciitilde{}\textasciitilde{} e*y4}
\StringTok{y5 \textasciitilde{}\textasciitilde{} e*y5}
\StringTok{\textquotesingle{}}
\NormalTok{fe\_sem.fit \textless{}{-}}\StringTok{ }\KeywordTok{sem}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ fe\_sem, }
                  \DataTypeTok{data =}\NormalTok{ dfw, }
                  \DataTypeTok{estimator =} \StringTok{"ML"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(fe\_sem.fit)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## lavaan 0.6-7 ended normally after 37 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of free parameters                         31
##   Number of equality constraints                     8
##                                                       
##   Number of observations                          1000
##                                                       
## Model Test User Model:
##                                                       
##   Test statistic                                30.138
##   Degrees of freedom                                32
##   P-value (Chi-square)                           0.561
## 
## Parameter Estimates:
## 
##   Standard errors                             Standard
##   Information                                 Expected
##   Information saturated (h1) model          Structured
...
\end{verbatim}
